### 2022-01-08 draft.tex
Deploying to gh-pages from @ gottacatchenall/ms_neutral_landscapes_jl@5fae74e2a5f1bfa0bf3c1d9a8d8a862b337a5613 🚀

We implement methods for generating change that are temporally
autocorrelated, spatially autocorrelated, or both.

@@

\(r\): rate, \(v\): variability, \(U\) matrix of draws from standard
\(\text{Normal}(0,1)\)

@@

@@

@@

>>>>

We implement methods for generating change that are temporally
autocorrelated, spatially-autocorrelated, or both.

@@

\(r\): rate, \(v\): variability, \(U\) matrix of draws from standard
\(\text{Normal}(0,1)\).

Here \(v\) replects the amount of temporal autocorrelation.

@@

Results in an expected value of change of \(r\) per timestep with
variance \(v\).

@@

Generate a matrix \(\delta\) with a NL generator.

@@

\begin{figure}
\centering
\includegraphics{./figures/temporal.png}
\caption{todo}
\end{figure}
